InformatiCup 2024 Ctrl-Alt-Defeat

### 2023-12-02 paper.tex
Initial draft of the method section

>>>>

\section{Introdution}

\section{Related work}

\subsection{Generating models}

\subsubsection{Image generating models}

\subsubsection{Text generating models}

\subsection{Detector models}

\subsubsection{Image detector models}

\subsubsection{Text detector models}

\section{Method}
To test and evaluate the effect of different data augmentation techniques on the detection capabilities of fake image or text detectors, we created a pipeline of three components: The first component is a generator, which is a model that is capable of generating fake images or text. The second component is a processor. After inputting a generated image or text, this component augments the data with a specified method. The third component contains a detector, which returns whether an input is a fake artefact or a real one. This way we can compare it to the ground truth, to evaluate the capabilities of the detector. By comparing the results with augmented artefacts and with the genrated artefacts without augmentation, we can see how effective different techniques are to trick ai detectors.

\section{Results}

\section{Discussion}

\section{Conclusion}
